Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Small fixes

\begin{definition}[Ignorant algorithm]
An algorithm $\calA$ for \textsc{Online Multiclass Linear Classification with
Bandit Feedback} is called \emph{ignorant} if for every $t=1,2,\dots,T$,
$p_t$ is determined solely by the sequence
$(x_{a_1}, y_{a_1}), (x_{a_2}, y_{a_2}), \dots, (x_{a_n}, y_{a_n})$
in the rounds $1 \le a_1 < a_2 < \dots < a_n < t$ in which
the algorithm makes a correct prediction.
\end{definition}

@@

Observe that in phase 1, the labels are equal to $1$ and in phase 2 the labels
are equal to $2$. Note that $(x_\tau, y_\tau)=(x_{\tau+1}, y_{\tau+1})= \dots =
(x_T, y_T) = (v_t, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as defined
in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and $w_2=u_\tau/2$
satisfy the conditions of strong linear separabaility.

>>>>

\begin{definition}[Ignorant algorithm]
An algorithm $\calA$ for \textsc{Online Multiclass Linear Classification with
Bandit Feedback} is called \emph{ignorant} if for every $t=1,2,\dots,T$,
$p_t$ is determined solely by the sequence
$(x_{a_1}, y_{a_1}), (x_{a_2}, y_{a_2}), \dots, (x_{a_n}, y_{a_n})$
of labeled examples
from the rounds $1 \le a_1 < a_2 < \dots < a_n < t$ in which
the algorithm makes a correct prediction.
\end{definition}

@@

Observe that in phase 1, the labels are equal to $1$ and in phase 2 the labels
are equal to $2$. Note that $(x_\tau, y_\tau)=(x_{\tau+1}, y_{\tau+1})= \dots =
(x_T, y_T) = (v_\tau, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as
defined in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and
$w_2=u_\tau/2$ satisfy the conditions of strong linear separabaility.
